\begin{problem}
  Show that a complete subspace of a metric space is a closed subset.
\end{problem}
\begin{answer}
  \begin{definition}
    A metric space $X$ is complete if every Cauchy sequence in $X$
    has a limit point in $X$.
  \end{definition}

  \begin{definition}
    A subset $S$ of a metric space $X$ is closed if $S$ contains all its limit points.
  \end{definition}

  \begin{claim}~\label{claim:3.1}
    Every convergent sequence is Cauchy.

    \begin{proof}
      Let $X$ be a metric space and $P \colonequals \braces{p_n}_1^\infty \subseteq X$ be a convergent sequence in $X$.
      Let $p \in X$ be the limit of $P$. \\
      For any $\epsilon > 0$, since $P$ converges to $p$,
      there exists $N \in \N$ such that
      $d(p_n, p) < \frac{\epsilon}{2}$ for all $n \geq N$.
      Therefore,
      \begin{align*}
        d(p_n, p_m) \leq d(p_n, p) + d(p, p_m) < \frac{\epsilon}{2} + \frac{\epsilon}{2} = \epsilon
      \end{align*}
      Therefore, $P$ is Cauchy.
    \end{proof}
  \end{claim}

  \begin{claim}~\label{claim:3.2}
    A complete subspace of a metric space is a closed subset.
    \begin{proof}
      Let $X$ be a metric space and $Y \subseteq X$ be a complete subspace of $X$.\\
      Let $P \colonequals \braces{p_n}_1^\infty \subseteq Y$ be an arbitrary
      convergent sequence in $Y$ (i.e. a sequence that has a limit).
      To show that $Y$ is closed, we need to show that any such $P$ has a limit point in $Y$.

      \step
      By claim~\ref{claim:3.1}, the convergence of $P$ implies that $P$ is Cauchy.
      Since $Y$ is complete by definition, and $P$ is Cauchy,
      $P$ has a limit point $p \in Y$.
      
      \step
      Since $P$ was arbitrary, $Y$ contains all its limit points,
      whenever limit points exist, so $Y$ is closed.
    \end{proof}
  \end{claim}
\end{answer}

